DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-01 paper/main.tex
Add initial platform comparison table/paragraph

\subsection{Platform Components}
We employ a small and relatively inexpensive RC car that is capable of performing basic automotive 
operations. However, the car we use doesn't replicate the capabilities of other autonomous vehicle 
platforms, as it is more simplistic in nature. Notably, the RC car we use only has three possible 
options in terms of turning: center, left, and right. As such, control of the car may be less precise at 
times, and may negatively affect performance. The car is capable of other operations that aren't used 
within the scope of this platform. Specifically, the car is able to drive in reverse and the driving 
speed can be changed. In our experiments, we have the RC car drive forward, and at a constant speed.

@@

>>>>

\subsection{Platform Components}

\begin{table*}[h]
  \centering
  \begin{tabular} {| l | l | l | l | l |}
    \hline
    \textbf{Platform} & \textbf{Picar} & \textbf{F1/10} & \textbf{NVIDIA DAVE-2}\\ \hline 
    Car & Mini RC Car (\$10) & Traxxas 1/10th car platform (\$299.97) & TBD\\ \hline
    Embedded system & Raspberry Pi 3 Model B (\$35.00) & NVIDIA Jetson TK1 (\$192.99) & NVIDIA DRIVE PX \\ \hline
    CPU & Cortex A-53 quad core & Cortex A-15 quad core & 8x Cortex A-57 quad core, 8x Cortex A-53 quad core \\ \hline
    Camera & Playstation Eye camera (\$6.99) & ZED camera (\$449.00) & 3x cameras\\ \hline
    Power Supply & Mobile battery (\$5.99) & Energizer battery pack (\$159.00) & TBD\\
    \hline
  \end{tabular}
  \caption{Comparison of components used in autonomous vehicle platforms.}
\end{table*}

We employ a small and relatively inexpensive RC car that is capable of performing basic automotive 
operations. However, the car we use doesn't replicate the capabilities of other autonomous vehicle 
platforms, as it is more simplistic in nature. Notably, the RC car we use only has three possible 
options in terms of turning: center, left, and right. As such, control of the car may be less precise at 
times, and may negatively affect performance. The car is capable of other operations that aren't used 
within the scope of this platform. Specifically, the car is able to drive in reverse and the driving 
speed can be changed. In our experiments, we have the RC car drive forward, and at a constant speed.

@@

Compared to other existing autonomous vehicle platforms, such as the F1/10 and NVIDIA DAVE-2, the Picar 
platform is capable of performing the same operations while using more cost inexpensive components. As 
shown by Table 1, the components selected for the Picar all cost considerably less than the other 
platforms when focusing on the common components (camera, power supply, etc.). Including the other 
components used in the F1/10 and DAVE-2, such as the additional sensors employed by both, the difference 
in cost would be even greater.
